\Large \bf Byteboy : A Byteman Companion application

### 2017-12-08 final-paper/paper.la_.tex
chore(paper): general clean-up and grammar checking

This paper presents Byteboy, a companion application suite for Byteman which includes a semi-automatic rule builder, a VS Code language extension, and a basic fuzz test generator for the Byteman scripting language.

@@

Writing bug free software is often easier said than done. Modern compilers and testing frameworks will often help developers minimize the number of bugs that make it into production environments, but there is no guarantee that the end result will be completely error free. For example, a Java program with poor exception handling coverage may pass a syntax check, but will crash if an unexpected exception type is thrown in response to an input. As a result, there is a need for tools that can diagnose and repair software bugs in runtime environments, and can interact with the program code in order to either create a temporary fix, or reveal the root cause of the error such that a proper fix can be developed.

@@

In this paper, we propose Byteboy\cite{byteboy}, a companion application for Byteman. Byteboy provides functionality for manual and semi-automatic rule generation, fuzz test generation, and a Visual Studio Code Byteman rule language extension. Byteboy was designed to improve the Byteman user experience from the point of rule inception, through to actually implementing and shipping the proposed bug-fixing rule file.

@@

Here, we wish to present Byteboy - a companion application for Byteman. Byteboy was designed to enhance the Byteman user experience by aiding the development of rules starting from the point of inception, through to the result of creating in a production-quality script.

The primary functionality of Byteboy is it's rule generator, which can be used in a manual or semi-automatic capacity. The manual rule generation using Byteboy is reminiscent of the Yeoman Generator\cite{yoman}, in which the program will guide new and first-time users through the process of writing rules. The semi-automatic rule generation actually performs an execution of the target program, and collects and aggregates information about the application performance and code structure to generate a set of plausible rules.

@@

The language extension is not yet currently available through the Extensions Marketplace, but future work efforts will be put forward towards a public release. Currently, the only method of installation would be to grab the {\tt byteman-language-extension} folder from the Byteboy repository, and copying it into the extensions folder located in the VS Code user settings folder. On Linux, this can be accomplished using the following command: 
\begin{center}
{\tt cp -r byteman-language-extension \textasciitilde/.vscode/extensions}
\end{center}
More instructions and details of usage can be found on the language-extension page of the Byteboy repository\cite{bytemanextension}.

@@

Currently, Byteboy has several limitations that confines it's use cases. For starters, Byteboy accepts a Java file with the extension {\tt .java} or {\tt .class} as input, however, many larger applications are not simply launched through the command-line using the {\tt java} command. Many popular Java applications may be packaged in {\tt .jar} format as an executable, or rely on larger build systems such as Maven and Gradle which makes the situation trickier.

>>>>

This paper presents Byteboy, a companion application suite for Byteman which includes a semi-automatic and automatic rule builder, a VS Code language extension, and a basic fuzz test generator for the Byteman scripting language.

@@

Writing bug free software is often easier said than done. Modern compilers and testing frameworks will often help developers minimize the number of bugs that make it into production environments, but there is no guarantee that the end result will be completely error free. For example, a Java program with poor exception handling coverage may pass a syntax check, but will crash if an unexpected exception type is thrown in response to an unexpected input. As a result, there is a need for tools that can diagnose and repair software bugs in runtime environments, and can interact with the program code in order to either create a temporary fix, or reveal the root cause of the error such that a proper fix can be developed.

@@

In this paper, we propose Byteboy\cite{byteboy}, a companion application for Byteman. Byteboy provides functionality for manual, semi-automatic, and automatic rule generation, fuzz test generation, and a Visual Studio Code Byteman rule language extension. Byteboy was designed to improve the Byteman user experience from the point of rule inception, through to actually implementing and shipping the proposed bug-fixing rule file.

@@

Here, we introduce Byteboy - a companion application for Byteman. Byteboy was designed to enhance the Byteman user experience by aiding the development of rules starting from the point of inception, through to the result of creating in a production-quality script.

The primary functionality of Byteboy is it's rule generator, which can be used in a manual or semi-automatic capacity. The manual rule generation using Byteboy is reminiscent of the Yeoman Generator\cite{yoman}, in which the program will guide new and first-time users through the process of writing rules. The semi-automatic rule generation actually performs an execution of the target program, and collects and aggregates information about the application performance and code structure to generate a set of plausible rules. The automatic rule generator creates a set of rules that can be used to trace the activity of a program in execution.

@@

The language extension is not yet currently available through the Extensions Marketplace, but future work efforts will be put forward towards a public release. Currently, the only method of installation would be to grab the {\tt byteman-language-extension} folder from the Byteboy repository\cite{byteboy}, and copying it into the extensions folder located in the VS Code user settings folder. On Linux, this can be accomplished using the following command: 
\begin{center}
{\tt cp -r byteman-language-extension \textasciitilde/.vscode/extensions}
\end{center}
More instructions and details of usage can be found on the language-extension page of the Byteboy repository\cite{bytemanextension}.

@@

Currently, Byteboy has several limitations that confines it's use cases. For starters, Byteboy accepts a Java program with the extension {\tt .java} or {\tt .class} as input, however, many larger applications are not simply launched through the command-line using the {\tt java} command. Many popular Java applications may be packaged in {\tt .jar} format as an executable, or rely on larger build systems such as Maven and Gradle which makes the situation trickier.
